Introduction text here... mpla mpla mpla

\par
--------------- IMPORTANT --------------- \par 
This version of the report is focused on the production of the main content for the thesis and only. That means that the language used in this early stage of the report should in no case be considered as final. After making sure that we achieved the desired result concerning the thesis' content, we will focus completely on improving the document in terms of language, syntax, formatting etc...
\par

\section{Photovoltaics in general}
General information about PV and the energy market in the moment and past. A few things about the future and the upcoming grouth of the solar energy area..

\section{PV measurements}
In order to characterize PV modules for efficiency etc, we need some measured values. Which values are important and why so?

\subsection{Voltage}
More information about the voltage output of a PV panel..

\subsection{Current}
More information about the current output of a PV panel.. Connection with the efficiency and the energy production

\subsection{Temperature}
Not so common, but important value. A few things about temperature "correction" and efficiency improvement (check Bert's work)

\subsection{Rest environmental conditions}
Humidity, pressure, wind etc
We are not working on that area but they are kind of important. So a few things for that area (check Bert's work again)

\section{State of the art}
Mention the available options for PV monitoring devices of the market, in the current moment

\section{Document structure}
How is the document structured. Brief description of each chapter maybe?\\
Bibliography testing right... here\cite{einstein}