Introduction text here...
mpla mpla mpla about the PCB and the measurements
Maybe mention that for more details about the actual programming or connection of the board, the reader can directly check the proper appendix chapter.

\section{Requirements}
The technical requirements of the measurement PCB.
They are connected with the project goals but are more specific and technical. 

\subsection{Logic and inputs}
After describing the nature of the inputs, there is clear that we need a ADC and therefore a CPU to co-work with that and handle all data and timing.
Atmega etc...

\section{Electrical measurements}
Maybe introduction with the general circuit for the measurements, without details.

\subsection{Voltage}
How the voltage is measured? Diagram, parts calculation etc

\subsection{Current}
How the current is measured? Diagram, parts calculation etc

\section{Temperature}
More details about the temperature measurements. Why this sensor and how the 1-wire works etc

\section{Time}
More details about the syncing and timing process of the whole board.
Diagram of the processes during the 1sec time frame?

\section{Isolation}
More details about isolation.
Why we need it and which ICs are used

\section{PCB Design}
Introduction about the PCB and the design process.
We start with prototypes and after the initial experiments we can proceed with the final design.
\subsection{Prototypes}
More details about all the prototype boards and how it evolved to the final PCB
\subsubsection{Electrical measurements}
Demo PCB board with 2 arduinos (plus the modules etc)
\subsubsection{Isolation test board}
Demo board for the two isolation ICs

\subsection{Final positioning/layout}
Image of the finished board..
Explain the position of each IC and the main traces (power, gnd etc)
\subsection{Connectors and Miscellaneous}
Brief description of each connector and few misc parts